---
title: "Forest Height-Cover Combinations for the MH"
author: "Randy Swaty"
date: "2/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Visual exploration of vegetation height and cover for the Michigamme Highlands

I used LANDFIRE 2014 data to make this quick sankey diagram that basically shows how much of the area is classified as trees 10-25m, with canopy closure of less than 70%.  This is not split by ecosystems (yet).  To me there is an uncharacteristic amount of canopy < 70%, which presents an opportunity.

Hover over segments to highlight patterns.


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}


library(networkD3)
library(dplyr)
library(readr)


links <- read_csv("mh_plantations2.csv")

nodes <- data.frame(
  name=c(as.character(links$source), 
         as.character(links$target)) %>% unique()
)

nodes <- data.frame(
  name=c(as.character(links$source), 
         as.character(links$target)) %>% unique()
)


links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

# Make the Network
p <- sankeyNetwork(Links = links, 
                   Nodes = nodes,
                   Source = "IDsource", 
                   Target = "IDtarget",
                   Value = "value", 
                   NodeID = "name", 
                   sinksRight=FALSE,
                   fontSize = 14)

p
```

